### 2018-08-25 introduction.tex

The present work introduces the online reprocessing simulation code, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}. 
It is also reports the application of the coupled SaltProc-SERPENT 2 system to 
the \gls{MSBR}, which represents the continuation of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective 
of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find 
the equilibrium core composition and core depletion. The additional objective is 
to compare predicted operational and safety parameters of the \gls{MSBR} at both 
the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
determined and \gls{MSBR} fuel cycle performance will be analyzed.

The \gls{MSBR} complex geometry is hard to describe in software input, and, 
usually, researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. Note that this study leverages extensive computational 
resources to avoid these geometric approximations and accurately capture 
breeding behavior. This article only discusses liquid-fueled \glspl{MSR}. 
Another challenge of the \glspl{MSR}, its delayed neutron precursor drift 
related to circulating liquid fuel, is not treated here.

>>>>

The present work introduces the online reprocessing simulation code, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyze \gls{MSBR} neutronics and fuel cycle to find 
the equilibrium core composition. The additional objective 
is to compare predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be 
determined and \gls{MSBR} fuel cycle performance will be analyzed.

The complex \gls{MSBR} geometry is challenging to describe in software input, 
and, 
usually, researchers make significant geometric simplifications to model it 
\cite{park_whole_2015}. This study leverages extensive computational 
resources to avoid these geometric approximations in order to accurately capture 
breeding behavior.
